Assignment 6 (Currently been modified on Nov 2)
========================================================
```{r include = FALSE}
opts_chunk$set(tidy = FALSE,
               comment=NA)
```

```{r echo=FALSE}
library(xtable)
html_print <- function(x, ..., digits = 0, include.rownames = FALSE, 
                       header=names(x)){
  # print html table with customized header, 
  # without permanently changing column names of the dataframe
  origHeader <- names(x)
  names(x) <- header
  print(xtable(x, digits = digits, ...), 
        type = 'html', include.rownames = include.rownames)
  names(x) <- origHeader
}
```

```{r results='asis', echo=FALSE}
#groupAlias <- read.table('result/groupAlias.tsv', sep='\t')
library(plyr)
dangerGrpDat <- read.table('result/TopDangerGroupDat.tsv', sep='\t', header=TRUE)
topGrpTotals <- ddply(dangerGrpDat, ~gname, summarize,
                      totalEvents=length(eventid),
                      totalKilled=sum(nkill, na.rm=TRUE)
                      )
```

These terrorist groups are the top `r nrow(topGrpTotals)` ranked by the total number of terrorist attacks they organized over the years.
```{r results='asis', echo=FALSE}
topGrpTotals <- arrange(topGrpTotals, totalEvents, decreasing=TRUE)
html_print(topGrpTotals, header=c('Group Name',
                                  'Total Events', 'Total Killed'),
           include.rownames = TRUE)

```

### The Rises and Falls Some of the Most Active Terrorist Group in History
![group impact](figure/group_impact_bar.svg)


![group impact violin](figure/group_impact_violin.svg)

![Number of killed against number of attacks](figure/group_pKilledvsAttacks.svg)



